Robust positively invariant sets for state dependent and scaled disturbances

### 2015-08-03 postreview.tex
Added remark about classification.

>>>>

Determining the map $v_{l,i}(x)$ for all admissible $x\in \mathcal X_0$ in general poses a great classification
challenge. 
Notice that in our calculations we can avoid determining the particular vertex $v_{l,i}(x)$ explicitly, it
suffices to determine the vertex determining a supporting hyperplane of $\mathcal X_{k+1}$, i.e.~$v_{l,i}^\ast(x)$. 
This can be done by adding all possible inequalities and applying a inequality reduction algorithm.
